Synergistic retrievals of ice in high clouds from elastic backscatter lidar, Ku-band radar and submillimeter wave radiometer observations

### 2023-05-16 RST/responseReviewers.tex

\documentclass[12pt]{article}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{longtable}
\author{Mircea Grecu and John E. Yorks}
\title{Synergistic retrievals of ice in high clouds
Response to Reviewers}
\date{}
\begin{document}
\maketitle

@@

will help mitigate them.}\\
\newline
We thank the reviewer for the uncertainty discussion. Yes, indeed the resolution of the simulated 
observations is that of the CloudSat radar, while the AOS instruments are expected to have different resolutions,

@@

which might impact results. In the revised manuscript, we included statements to convey this aspect.
We agree that the assumed electromagnetic scattering properties assumed in the study, although
reasonable, may contain significant uncertainties.  We acknowledge this aspect in the revised manuscript 
as well. Regarding the measurement uncertainties, we realistically account for them in the radar and radiometer simulations,

@@

model of space-borne lidar measurement uncertainties was developed in \cite{liu2006}, but its parameters are
difficult to reliably quantify from theoretical considerations based on instrument expectations alone. Instead, we
assume a simple multiplicative error model, with the multiplicative factor model as a log-normally distributed random
variable with 0.0 mean and 0.1 standard deviation, which results in observation uncertainties similar to those in

@@

Line 38: Where is 8.0 dBZ coming from? There should be a citation here, or it should be stated that this is 
an estimate of the radar’s expected sensitivity.}\\
\newline
This is an estimate of the radar’s expected sensitivity provided by Japan Aerospace Exploration Agency (JAXA), which is
the AOS International partner contributing the Ku-band radar in the inclined orbit.\\

@@

\newline
We agree. We do not consider CloudSat retrievals uncertainty or bias free, but we prefer them because
they are consistent with an observed vertical distribution of reflectivity at W-band. The vertical distributions of radar reflectivity
derived from satellite or ground-based observations are generally difficult to reproduce by model simulations.
We added statements
to this effect in the revised manuscript (bottom of page 3 and top part of page 4).\\

@@

\newline
We agree. As described explained above, our  objective was to derive IWC distributions consistent with the observed vertical distribution of
CloudSat reflectivity, without implying that the resulting distributions are uncertainty or bias free.  To make the performance
assessment more realistic, in the revised version of the manuscript, we perturbed the $N_w$ value (which in the first version 
of the manuscript was
parameterized as a function of height) used in the derivation of IWC as a function of observed CloudSat reflectivity by a random log-normally

@@

distributed factor. This accounts for uncertainties in the PSDs (at least from the perspective of the normalized PSD framework) and 
makes the evaluation realistic. Nevertheless, as observed by the reviewer, the electromagnetic scattering properties are 
an additional source of uncertainty.  We included additional statements in the manuscript 
(bottom of page 8 and top of page 9) to describe $N_w$ perturbation approach and

@@

 supported this statement, or any equations that resembled Eq. (1). Please add further explanation, either here 
 or in an appendix, to help the reader follow your logic.}\\
\newline
We apologize for the confusion. Testud et al. (2001) only show that normalization by $N_w$ ($N_0^*$ in their notation) 
explains the variability

@@

in Z-R relationships (fig. 9d). Ferreira et al. (2001) \cite{ferreira2001} make the more general statement that any two integrated rainfall parameters ($X$, $Y$) 
may be related through a power law of the form $X = m N_w^{(1-n)} X^n$, where $m$ and $n$ are constants almost independent of $N_w$. Delanoe et al. (2014)
 \cite{delanoe2014} show that the same relationship holds for ice PSDs. We added statements to this effect in the paragraph following
 the definition of Equation (1).\\

@@

we reduced the number of classes to 18 to make the classification and the Ensemble Kalman Filter more robust.  
For consistency and simplicity in the revised manuscript we derive IWC-Z relationships 
for each CloudSat radar bin, with the bins indexed relative to the freezing level bin.  The relative height is now defined as the distance
between the height of the associated bin relative to the freezing level.  Results are rather similar, although the overall performance is
degraded to some degree.\\

@@

data in Fig. 2? This needs to be clarified.}\\
\newline
Yes, we fit a line to determine the variation of $ln(a)$ as a function of height and then divide the slope by $(1-b)$ to get the variation of
$ln(N_w)$ as a function of height. We added explanations in the paragraph preceding Equation (2).\\

@@

\textit{1. To address the first-mentioned issue above, the authors should include radar-only, lidar-only, and radar-lidar 
    retrieval in their analysis.}\\
\newline
We agree with the reviewer. The revised manuscript includes radar-only, lidar-only, and other combinations of instruments retrievals
 in the analysis.  Shown 

@@

\newline
We agree with the reviewer. The revised manuscript includes a randomization of the parametrization of the multiplicative factor $a$.  Specifically,
we randomly perturb $N_w$ by multiplying its parameterized value with log-normally distributed
random variable with zero mean a standard deviation of 0.5.  As explained above, we use a Gaussian smoothing filter to impose a
vertical auto-correlation in
$N_w$ similar to that observed in field experiments. This is explained in lines 153 through 162 of the revised manuscript.\\

@@

In AOS terminology, high clouds are convectively generated high clouds \cite{braun2022}. Such clouds are the result of strong vertical mass transport 
from the lower troposphere and horizontal transport in the upper troposphere.  While preponderantly consisting of ice, high clouds may exhibit 
liquid phased hydrometeors. To make it clear upfront that we are not considering mixed-phase clouds in this study, we included ice in the title.
We included clarifying statements on the definition of high-clouds in the manuscript introduction. \\

@@

assume a simple multiplicative error model, with the multiplicative factor model as a log-normally distributed random
variable with 0.0 mean and 0.1 standard deviation, which result in observation uncertainties similar to those in
the in evaluation study of the Cloud-Aerosol Transport System (CATS) lidar-system. 
We acknowledge the limitations of this approach in the revised manuscript.  Statements to this effect are included in
the paragraphs devoted to the descriptions of the forward models. \\ 

@@

    is also generally true for ice particles.}\\
\newline
The impact of normalization on Z-IWC relationship is shown in \cite{delanoe2014}. Soft spheres were assumed and the Mie solution was used in \cite{delanoe2014}
to derive reflectivities from observed Particle Size Distributions, but \cite{chase2021}  used more advanced backscattering models to calculate Z from

@@

observed PSDs.  Their calculations are publicly available at https://github.com/dopplerchase/Chase\_et\_al\_2021\_NN and may be used to confirm the contraction
of the ($Z/N_w$,$IWC/N_w$) distribution to almost one-to-one relationships.  As explained in the manuscript, we use the self-similar Rayleigh-Gans approximation
to model the backscattering property of ice particles but get a normalization behavior similar to that anticipated by Testud et al. (2001),
shown in \cite{delanoe2014} and exhbited in the \cite{chase2021} database.
We added statements to this effect in the paragraph following the definition of Equation (1).\\

@@

the coefficients $a$ as a function of the height of the class-average IWC peak for each class. We subsequently reduced the number of classes 
to 18 to make the classification and 
estimation process more robust. However, for consistency and simplicity in the revised manuscript we derive IWC-Z relationships 
for each CloudSat radar bins, with the bins indexed relative to the freezing level bin.  The relative height is defined as the distance
between the height of the associated bin relative to the freezing level.  Results are rather similar, although the overall performance is
degraded to some degree.\\

@@

\textit{7. Fig. 3: Please clarify: Why is the distribution of radar reflectivities going to zero towards the freezing level? 
    What about precipitating clouds?}\\
\newline
We selected only CloudSat reflectivity profiles with no echo at and below the freezing level.  

@@

is estimated, the authors must use a priori assumptions to resolve the ambiguity in the retrievals.}\\
\newline
We derive the IWC as a function of CloudSat $Z$ and $N_w$.  The $N_w$ is given by the vertical parameterization and perturbed using the random model
described above and in the revised manuscript.  Specifically, given $N_w$ and the associated $Z$ at W-band, we estimate $IWC/N_w$ as a function of $Z/N_w$ using the
normalized tables and then derive $IWC$ from $IWC/N_w$ and $N_w$. We added a statement in the manuscript to clarify this point.\\

@@

\textit{10. l. 203: I don't think that 200,000 profiles can be considered a large dataset by today's standards.}\\
\newline
We agree that 200,000 profiles is not a large dataset by today's standards.  However, these profiles are derived from a month of CloudSat observations.
Specifically, all CloudSat and 2C-ICE product files from June 2019 were processed, and only profiles with no cloud echo at 
and below the freezing level
were selected. Moreover, in the first version of the manuscript, we imposed the rather artificial condition that at least 
three CloudSat reflectivity pixels above the freezing level be classified as cloud for a profile to be select.
These two conditions resulted in a rather small number of profiles. 
We removed the second condition is the selection of profiles used in the revised analysis. This resulted in 
about 800,000 of profiles. While 75\% of these profiles consist of at most three pixels, there is sufficient
vertical variability in the selected profiles to derive meaningful conclusions. 
We added statements in the manuscript to clarify this aspect.\\

### 2023-05-16 RST/RSTManuscript.tex
Review May 15

\title{Synergistic retrievals of ice in clouds from elastic backscatter lidar, 
Ku-band radar and submillimeter wave radiometer observations}

@@

would allow the study of atmopsheric processes at sub-daily time scales, with an emphasis on deep

@@

\subsection{Assumptions and forward models}
To quantify the number of ice particles in an elementary atmospheric volume as a function of their size, we use
normalized gamma functions \citep{bringi2003}.  The benefit of normalized gamma functions is that they 
encapsulate the variability of Ice Water Content (IWC) - reflectivity relationship into a single parameter,
i.e. the 
normalized Particle Size Distribution (PSD) intercept \citep{testud2001,bringi2003}. The normalized
PSD intercept is defined as $N_w=\frac {4^4} {\pi \rho_w} \frac {IWC} {D_m^4}$, where $IWC$ is the ice water 
content associated with the PSD, and $D_m$ is the mass weighted mean diameter.  \cite{testud2001} showed 
that the variability in IWC reflectivity (Z) relationships may be fully explained by variability in $N_w$, and 
that a formula of the type
\begin{equation}
IWC=N_w^{1-b}a_{norm} Z^b \label{eq:1}
\end{equation}
perfectly explains the relationships between IWC and Z calculated from observed PSDs. 
Although the initial work of \cite{testud2001} was limited to rain and only hinted about the applicability
of the normalization concept to ice observations, subsequent studies showed that parameterizations
of type (\ref{eq:1}) extended to ice \citep{ferreira2001,delanoe2014}.
Equation (\ref{eq:1}) is not 
sufficient to derive accurate, unbiased estimates of ice water contents, because $N_w$ varies considerably in 
time and space. Nevertheless, multiple studies showed that it is beneficial to parameterize $N_w$ as a function 
of various variables, such as temperature \citep{hogan2006retrieval, delanoe2008variational,deng2010tropical}, 
rather than using $N_w$ independent reflectivity ice relations.  In this study, we parameterize
$N_w$ as a function of temperature based on the CloudSat 2C-ICE product \citep{deng2010tropical,deng2013evaluation}.  
Specifically, we cluster, based on similarity (quantified through the evaluation of the Euclidian distance between profiles), 
a large set 2C-ICE profiles into 18 classes using a k-Means 
procedure. The mean IWC profiles associated with the 18 classes are shown in continuous lines in Figure 1.  
Our estimates, derived using PSD assumptions and electromagnetic scattering calculations that enable 
accurate and physically consistent simulations of radar observations at Ku-band and radiometer observations of 
submillimeter-wave frequencies are also shown in Figure 1. These estimates are based on the self-similarity 
Rayleigh-Gans approximation (SSRGA) of \cite{hogan2017ssrga}. Details regarding the
estimation process are provided in the following paragraphs.  As apparent in Figure 1, the CS and SSRGA estimates are in good 
agreement.  Some discrepancies due to differences between the SSRGA $N_w$ parameterization and the CS 2C-ICE 
"a priori assumptions" are also apparent, but they are not deemed critical in this study, whose objective is 
the investigation of synergistic lidar, Ku-band radar and submillimeter-wave radiometer retrievals, because the 
outcome is not likely to be sensitive to such details.
\begin{figure}[t]
    \centering
    \includegraphics[width=0.75\textwidth,angle=0]{./Figs/fig01.png}\\
    \caption{Mean CS IWC profiles for 18 classes derived using the k-Means clustering algorithm. For a 
    compressed but intelligible representation, three classes are shown in different colors in each panel.
    The associated 
    mean profiles derived from CS reflectivity observations using the SSRGA scattering calculations 
    and $N_w$ parameterization developed in this study are shown using symbol *. The vertical coordinate 
    is defined relative to the freezing level.}\label{f1}
\end{figure}

@@

For the determination of reference $a$ and $b$ values to be used with Equation (\ref{eq:1}), we assume that 
PSDs are normalized gamma  distributions with $N_w=0.08cm^{-4}$ and $\mu=2$ and calculate 
\begin{equation}
 Z=\frac {\lambda ^4} {\pi ^5 |K_w|^2} \int_0^{\infty} N(D,D_m) \sigma _b(D) dD
\end{equation}
where $\lambda$ is the radar frequency, $|K_w|$ is the dielectric factor of water, $N(D,D_m) dD$ is the number 
of ice particles of diameter with D and D+dD per unit volume, $D_m$ is the mass weighted mean diameter of the 
distribution, and $\sigma _b(D)$ is the backscattering cross-section of ice particle of diameter $D$. The mass 
weighted mean diameter is equidistantly sampled to span the entire range of IWC values in the CS 2C-ICE dataset.
The assumed mass-size relation is that of \cite{brown1995improved} because it works well with the 
SSRGA scattering calculations \citep{heymsfield2022impacts}.  The open source software scatter-1.1 of \citep{scatter-1.1}
is used to provide the actual scattering properties.   
To improve the representation of microphysical variability in the study, we don't assume the values of $N_w$ given
by the 2C-ICE based parametrization described above as the true values. Instead, we perturb them by multiplication 
with a log-normally distributed random variable with 0.0 mean a standard deviation of 0.5.  The 
perturbations are vertically correlated. Specifically, normal random variables with zero mean and a standard deviation
of 1.0 are generated and then passed through a Gaussian smoothing filter \citep{nixon2019} with a size of two radar bins. The perturbation
vector is then rescaled to have a standard deviation of 0.5.  The perturbations are then exponentiated and multiplied
with the 2C-ICE based $N_w$ values to produce the final $N_w$ values.  The filter size and noise magnitude are chosen
to roughly mimic the observed variability in $N_w$ derived from in situ observations of PSDs, such as those described
in \cite{heymsfield2022impacts}. In addition, we are adding a random noise of
0.0 mean and 0.5 dB standard deviation to the calculated reflectivity values, which is consistent with the expected
performance of a space-borne Ku-band radar system \citep{takahashi2008}.  Nevertheless, it should be noted that the
uncertainties in the reflectivity calculations are likely to be even larger, given that the SSRGA theory although 
quite accurate cannot possibly capture the entire range of uncertainties in the scattering properties of ice particles.
Specifically, the SSRGA calculations were carried out assuming ice particles consisting of aggregates of 
bullet rosettes, columnar crystals, and plates.

@@

Shown in Figure 3 are the distributions of simulated Ku-band radar reflectivity and 
lidar backscatter as function of height above the freezing level.
As apparent in the figure, the IWCs associated with detectable Ku-band reflectivity
signal are likely to
occur near mostly around 3.0 km above the freezing level, while the lidar backscatter
distribution exhibits a peak at around 6.0-7.0 km
above the freezing level, which is consistent with the fact the lidar observations
are strongly attenuated in the bottom part of the cloud.  The vertical resolutions of
the radar and lidar observations are the same, i.e. 240 m, and the same as the resolution of the
CS observations upon which they are based. In reality, the radar and lidar observations are likely to have
different vertical resolutions and footprint sizes, which would need to be accounted for in a more 
realistic study.  It should be noted though that the AOS radars and radiometers are expected to achieve
Nyquist sampling, which enables resolution enhancement \citep{early2001image}.  Nevertheless, differences
in the vertical resolutions of the radar and lidar observations and differences in the footprint sizes
may deteriorate the performance of the retrieval algorithm.

@@

The radiometer observations are calculated using a one-dimensional efficient, but accurate, radiative transfer 
solver based on Eddington's approximation \citep{kummerow1993edd}. The Eddington's approximation has been found to work 
well in cloud and precipitation retrieval application despite its simplicity relative to more general (but also 
computationally intensive) approaches such as Monte Carlo radiative transfer solvers \citep{liu1996three} 
It should be noted tough that the phase functions of ice particles tend to be highly asymmetric at 
sub-millimeter wave frequencies. For radiative transfer solutions based on the Eddington's approximation to be 
accurate, it is necessary that the delta-scaling approach \citep{joseph1976delta} be employed. The delta-scaling 
approach transforms the initial radiative transfer equation into an equivalent one characterized by a less 
asymmetric scattering function and more extinction, which makes the solution Eddington approximation more stable 
and accurate. The absorption due to water vapor and other gases is quantified using the Rosenkranz model 
\citep{rosenkranz1998}.  The water vapor, temperature, and pressure distributions are derived based on a WRF 
simulation of summer convection over the United States.  Specifically, the water vapor, temperature, and 
pressure profiles associated with times and areas where the model produces anvils are selected and clustered 
into 40 classes using the k-Means approach.  The mean extinction profiles at the radiometer frequencies are 
calculated for every class 
and used in process of calculating the brightness temperatures from the estimated ice profiles using a simple 
Monte Carlo procedure.  That is, given a retrieved ice profile and its scattering property, an anvil class 
and its associated absorption, temperature, and pressure profiles are randomly selected and attached to the 
ice scattering properties. To make the procedure physically meaningful, temperature rather than height is 
used in the ice scattering-gas absorption collocation process.  The surface emissivities are randomly chosen between 
0.8 and 1.0 and assumed constant for all radiometer frequencies.  Brightness temperatures are calculated at 
%89-, 183.31 ± 1.1, and 325.15 ± 1.5 GHz,
all frequencies of the 10 channels of the SAPHIR-NG 
radiometer envisioned to be deployed in the AOS mission \citep{brogniez2022time}.  One of the frequencies is 
89-GHz, while the others are centered on the 183.31, and 325.15 GHz water vapor absorption lines. Details are
provided in Table \ref{t_sensors}.  Errors in the radiometer observations are modeled assuming a 
Noise-Equivalent-Delta-T (NEDT) of 1K, which is a readily achievable level for modern satellite radiometers \cite{draper2015}.

The processing steps used to process the CS reflectivity observations and calculate the lidar, Ku-band and 
submillimeter-wave radiometer observations may be summarized as follows:
\begin{enumerate}
\item Derivation of physically consistent radar and radiometer lookup tables to relate basic radar and 
radiometer properties (e.g. reflectivity, attenuation, extinction, scattering-albedo, etc.) to PSD parameters 
such as $IWC$ and $D_m$. The tables are derived for a single of $N_w$, but are usable with any value of 
$N_w$ using the "normalization" operations described in \citep{grecu2011}.
\item Derivation of $N_w$-relative height parameterization using the 2C-ICE product.
\item Estimation of IWC and related PSD parameters from CS W-band radar observations, using the tables 
constructed
in Step 1 and parameterization derived in Step 2.
\item Calculation of lidar, Ku-band radar and radiometer observations from the estimates derived in Step 3 
and the tables obtained in Step 1, and extended with non-zero 2C-ICE estimates for the radar bins characterized by no echo
above the noise level.
\end{enumerate}

@@

Further insight into the radiometer-only estimation performance may be derived by defining the ice profile gravity center 
(GC) as $z_{GC}=\frac {\int_0^{Z_{top}}zIWC(z)dz} {\int_0^{Z_{top}}IWC(z)dz}$, where $z$ is the distance relative to 
the freezing level, the $Z_{top}$ is the distance from the top of the atmosphere to the freezing level.  
Shown in Figure \ref{f6} is the frequency of IWC gravity center
estimated from radiometer-only observations as a function of its true value.  It may be observed in the figure that while 
the true IWC gravity center exhibits quite a broad distribution, the one retrieved from the radiometer-only 
observations exhibits a multimodal narrow distribution. Moreover, there is almost no correlation between the retrieved 
and the true IWC gravity center.  This is another indication that, while the total amount of ice may be reasonably 
estimated from radiometer-only observations, its vertical distribution can not be 
accurately determined from 
radiometer-only observations.

@@

\subsection{Active instrument retrievals}
Although retrievals from the lidar-only or radar-only observations are not expected to be as accurate as those from
radiometer-only observations, the lidar observations being subject to severe attenuation while the radar observations
being limited by its sensitivity, they are nevertheless insightful.
\subsection{Synergistic retrievals}

@@

Shown in Figure \ref{f7} is the distribution of the synergistic IWP estimates as a function of their true
values.  As apparent in the figure, the synergistic IWP estimates are more accurate than the radiometer-only
estimates. At the same time, as apparent in Figure \ref{f8}, the retrieved conditional mean IWC for the 
18 classes described section 2a and shown in Figure \ref{f1} are in significantly better (almost perfect)
agreement with the true IWC profiles than those derived from radiometer-only observations.  Furthermore,
as seen in Figure \ref{f9} the synergistic IWC gravity center estimates are in very good agreement with 
the true IWC gravity center.

>>>>

\title{Synergistic retrievals of ice in high clouds from elastic backscatter lidar, 
Ku-band radar and submillimeter wave radiometer observations}

@@

would allow the study of atmospheric processes at sub-daily time scales, with an emphasis on deep

@@

\subsection{Assumptions and forward models}
To quantify the number of ice particles in an elementary atmospheric volume as a function of their size, we use
normalized gamma functions \citep{bringi2003}.  The benefit of normalized gamma functions is that they 
encapsulate the variability of Ice Water Content (IWC) - reflectivity relationship into a single parameter,
i.e. the 
normalized Particle Size Distribution (PSD) intercept \citep{testud2001,bringi2003}. The normalized
PSD intercept is defined as $N_w=\frac {4^4} {\pi \rho_w} \frac {IWC} {D_m^4}$, where $IWC$ is the ice water 
content associated with the PSD, and $D_m$ is the mass weighted mean diameter.  \cite{testud2001} showed 
that the variability in IWC reflectivity (Z) relationships may be fully explained by variability in $N_w$, and 
that a formula of the type
\begin{equation}
IWC=N_w^{1-b}a_{norm} Z^b \label{eq:1}
\end{equation}
perfectly explains the relationships between IWC and Z calculated from observed PSDs. 
Although the initial work of \cite{testud2001} was limited to rain and only hinted about the applicability
of the normalization concept to ice observations, subsequent studies showed that parameterizations
of type (\ref{eq:1}) extended to ice \citep{ferreira2001,delanoe2014}.
However, equation (\ref{eq:1}) is not 
sufficient to derive accurate, unbiased estimates of ice water contents, because $N_w$ varies considerably in 
time and space. Nevertheless, multiple studies showed that it is beneficial to parameterize $N_w$ as a function 
of various variables, such as temperature \citep{hogan2006retrieval, delanoe2008variational,deng2010tropical}, 
rather than using $N_w$ independent reflectivity ice relations.  In this study, we parameterize
$N_w$ as a function of temperature based on the CloudSat 2C-ICE product \citep{deng2010tropical,deng2013evaluation}.  
Specifically, we cluster, based on similarity (quantified through the evaluation of the Euclidian distance between profiles), 
a large set 2C-ICE profiles into 18 classes using a k-Means 
procedure. The mean IWC profiles associated with the 18 classes are shown in continuous lines in Figure 1.  
Our estimates, derived using PSD assumptions and electromagnetic scattering calculations that enable 
accurate and physically consistent simulations of radar observations at Ku-band and radiometer observations of 
submillimeter-wave frequencies are also shown in Figure 1. These estimates are based on the self-similarity 
Rayleigh-Gans approximation (SSRGA) of \cite{hogan2017ssrga}. Details regarding the
estimation process are provided in the following paragraphs.  As apparent in Figure 1, the CS and SSRGA estimates are in good 
agreement.  Some discrepancies due to differences between the SSRGA $N_w$ parameterization and the CS 2C-ICE 
"a priori assumptions" are also apparent, but they are not deemed critical in this study, whose objective is 
the investigation of synergistic lidar, Ku-band radar and submillimeter-wave radiometer retrievals, because the 
outcome is not likely to be sensitive to such details.
\begin{figure}[t]
    \centering
    \includegraphics[width=0.75\textwidth,angle=0]{./Figs/fig01.png}\\
    \caption{Mean CS IWC profiles for 18 classes derived using the k-Means clustering algorithm. For a 
    compressed but intelligible representation, three classes are shown in different colors in each panel.
    The associated 
    mean profiles derived from CS reflectivity observations using the SSRGA scattering calculations 
    and $N_w$ parameterization developed in this study are shown using symbol *. The vertical coordinate 
    is defined relative to the freezing level.}\label{f1}
\end{figure}

@@

For the determination of reference $a$ and $b$ values to be used with Equation (\ref{eq:1}), we assume that 
PSDs are normalized gamma  distributions with $N_w=0.08cm^{-4}$ and $\mu=2$ and calculate 
\begin{equation}
 Z=\frac {\lambda ^4} {\pi ^5 |K_w|^2} \int_0^{\infty} N(D,D_m) \sigma _b(D) dD
\end{equation}
where $\lambda$ is the radar frequency, $|K_w|$ is the dielectric factor of water, $N(D,D_m) dD$ is the number 
of ice particles of diameter with D and D+dD per unit volume, $D_m$ is the mass weighted mean diameter of the 
distribution, and $\sigma _b(D)$ is the backscattering cross-section of ice particle of diameter $D$. The mass 
weighted mean diameter is equidistantly sampled to span the entire range of IWC values in the CS 2C-ICE dataset.
The assumed mass-size relation is that of \cite{brown1995improved} because it works well with the 
SSRGA scattering calculations \citep{heymsfield2022impacts}.  The open source software scatter-1.1 of \citep{scatter-1.1}
is used to provide the actual scattering properties.   
To improve the representation of microphysical variability in the study, we do not assume the values of $N_w$ given
by the 2C-ICE based parametrization described above as the true values. Instead, we perturb them by multiplication 
with a log-normally distributed random variable with 0.0 mean a standard deviation of 0.5.  The 
perturbations are vertically correlated. Specifically, normal random variables with zero mean and a standard deviation
of 1.0 are generated and then passed through a Gaussian smoothing filter \citep{nixon2019} with a size of two radar bins. The perturbation
vector is then rescaled to have a standard deviation of 0.5.  The perturbations are then exponentiated and multiplied
with the 2C-ICE based $N_w$ values to produce the final $N_w$ values.  The filter size and noise magnitude are chosen
to roughly mimic the observed variability in $N_w$ derived from in situ observations of PSDs, such as those described
in \cite{heymsfield2022impacts}. In addition, we are adding a random noise of
0.0 mean and 0.5 dB standard deviation to the calculated reflectivity values, which is consistent with the expected
performance of a space-borne Ku-band radar system \citep{takahashi2008}.  Nevertheless, it should be noted that the
uncertainties in the reflectivity calculations are likely to be even larger, given that the SSRGA theory although 
quite accurate cannot possibly capture the entire range of uncertainties in the scattering properties of ice particles.
Specifically, the SSRGA calculations were carried out assuming ice particles consisting of aggregates of 
bullet rosettes, columnar crystals, and plates.

@@

Shown in Figure 3 are the distributions of simulated Ku-band radar reflectivity and 
lidar backscatter as function of height above the freezing level.
As apparent in the figure, the IWCs associated with detectable Ku-band reflectivity
signal are likely to
occur near mostly around 3.0 km above the freezing level, while the lidar backscatter
distribution exhibits a peak at around 6.0-7.0 km
above the freezing level, which is consistent with the fact the lidar observations
are strongly attenuated in the bottom part of the cloud.  It should be noted that, consistently with the objective of
 this study, only CS reflectivity profiles with no echo at or below the freezing level were selected
and used in the calculation of Ku-band reflectivity distributions shown in Figure \ref{f3}.
The vertical resolutions of
the radar and lidar observations are the same, i.e. 240 m, and the same as the resolution of the
CS observations upon which they are based. In reality, the radar and lidar observations are likely to have
different vertical resolutions and footprint sizes, which would need to be accounted for in a more 
realistic study.  It should be noted though that the AOS radars and radiometers are expected to achieve
Nyquist sampling, which enables resolution enhancement \citep{early2001image}.  Nevertheless, differences
in the vertical resolutions of the radar and lidar observations and differences in the footprint sizes
may deteriorate the performance of the retrieval algorithm.

@@

The radiometer observations are calculated using a one-dimensional efficient, but accurate, radiative transfer 
solver based on Eddington's approximation \citep{kummerow1993edd}. The Eddington's approximation has been found to work 
well in cloud and precipitation retrieval application despite its simplicity relative to more general (but also 
computationally intensive) approaches such as Monte Carlo radiative transfer solvers \citep{liu1996three} 
It should be noted tough that the phase functions of ice particles tend to be highly asymmetric at 
sub-millimeter wave frequencies. For radiative transfer solutions based on the Eddington's approximation to be 
accurate, it is necessary that the delta-scaling approach \citep{joseph1976delta} be employed. The delta-scaling 
approach transforms the initial radiative transfer equation into an equivalent one characterized by a less 
asymmetric scattering function and more extinction, which makes the solution Eddington approximation more stable 
and accurate. The absorption due to water vapor and other gases is quantified using the Rosenkranz model 
\citep{rosenkranz1998}.  The water vapor, temperature, and pressure distributions are derived based on a WRF 
simulation of summer convection over the United States.  Specifically, the water vapor, temperature, and 
pressure profiles associated with times and areas where the model produces anvils are selected and clustered 
into 40 classes using the k-Means approach.  The mean extinction profiles at the radiometer frequencies are 
calculated for every class 
and used in process of calculating the brightness temperatures from the estimated ice profiles using a simple 
Monte Carlo procedure.  That is, given a retrieved ice profile and its scattering property, an anvil class 
and its associated absorption, temperature, and pressure profiles are randomly selected and attached to the 
ice scattering properties. To make the procedure physically meaningful, temperature rather than height is 
used in the ice scattering-gas absorption collocation process.  The surface emissivities are randomly chosen between 
0.8 and 1.0 and assumed constant for all radiometer frequencies.  Brightness temperatures are calculated at 
%89-, 183.31 ± 1.1, and 325.15 ± 1.5 GHz,
all frequencies of the 10 channels of the SAPHIR-NG 
radiometer envisioned to be deployed in the AOS mission \citep{brogniez2022time}.  One of the frequencies is 
89-GHz, while the others are centered on the 183.31, and 325.15 GHz water vapor absorption lines. Details regarding
the radiometer and the active instruments are
provided in Table \ref{t_sensors}.  Errors in the radiometer observations are modeled assuming a 
Noise-Equivalent-Delta-T (NEDT) of 1K, which is a readily achievable level for modern satellite radiometers \cite{draper2015}.

The processing steps used to process the CS reflectivity observations and calculate the lidar, Ku-band and 
submillimeter-wave radiometer observations may be summarized as follows:
\begin{enumerate}
\item Derivation of physically consistent radar and radiometer lookup tables to relate basic radar and 
radiometer properties (e.g. reflectivity, attenuation, extinction, scattering-albedo, etc.) to PSD parameters 
such as $IWC$ and $D_m$. The tables are derived for a single of $N_w$, but are usable with any value of 
$N_w$ using the "normalization" operations described in \citep{grecu2011}.
\item Derivation of $N_w$-relative height parameterization using the 2C-ICE product.
\item Estimation of IWC and related PSD parameters from CS W-band radar observations, using the tables 
constructed Step 1, and $N_w$ profiles derived through parameterization obtained in Step 2 and perturbed using the random model 
described above. Specifically, given $N_w$ and the associated $Z$ at W-band, we estimate $IWC/N_w$ as a function of $Z/N_w$ using the
normalized tables and then derive $IWC$ from $IWC/N_w$ and $N_w$.
\item Calculation of lidar, Ku-band radar and radiometer observations from the estimates derived in Step 3 
and the tables obtained in Step 1, and extended with non-zero 2C-ICE estimates for the radar bins characterized by no echo
above the noise level.
\end{enumerate}

@@

Further insight into the radiometer-only estimation performance may be derived by defining the ice profile gravity center 
(GC) as $z_{GC}=\frac {\int_0^{Z_{top}}zIWC(z)dz} {\int_0^{Z_{top}}IWC(z)dz}$, where $z$ is the distance relative to 
the freezing level, the $Z_{top}$ is the distance from the top of the atmosphere to the freezing level.  
Shown in Figure \ref{f6} is the frequency of IWC gravity center
estimated from radiometer-only observations as a function of its true value.  It may be observed in the figure that while 
the true IWC gravity center exhibits quite a broad distribution, the one retrieved from the radiometer-only 
observations exhibits a multimodal narrow distribution. Moreover, there correlation between the retrieved 
and the true IWC gravity center is rather low.  This is another indication that, while the total amount of ice may be 
reasonably estimated from radiometer-only observations, its vertical distribution can not be 
accurately determined from radiometer-only observations.

@@

\subsection{Active instrument retrievals}

Although retrievals from the lidar-only or radar-only observations are not expected to be as accurate as those from
radiometer-only observations, the lidar observations being subject to severe attenuation while the radar observations
being limited by its sensitivity, they are nevertheless insightful. This is because quantifying the limitations of
retrievals from active instruments may be used to better assess  the benefits of synergistic retrievals.  Shown in
top of row of Figure \ref{f7} are the distributions of IWP estimated from lidar-only and radar-only observations 
as a function of their true values. As apparent in the figure, and as expected, the lidar-only retrievals tend to
be accurate for IWP values smaller than 50 g/m$^2$, while the radar-only retrievals tend to be reliable only for large
IWP values on the order of hundreds of g/m$^2$.  Not that the radar-only retrievals exhibit a bimodal distributions,
with a broad distribution of real IWP values associated with a single retrieved IWP value.  This is a consequence
of the fact that there is a large number of atmospheric profiles characterized by not necessarily small IWP values that
are not associated with detectable radar signals. The results shown in the top row of Figure \ref{f7} are conditional on
either the CALIOP lidar or CS radar observations detecting ice, and so are the radar-only retrievals. However, the 
indiscriminate application of a Ku-band radar-only retrieval procedure to the entire dataset may result in significant
overestimation because clear skies would be associated with the same IWP value as ice clouds with reflectivity signal 
below the detection threshold. On the other hand, limiting the application of the radar-only retrieval procedure to atmospheric profiles
with detectable ice clouds would result in a significant underestimation, as a large number of atmospheric profiles
with ice clouds would be associated with zero IWP.  From this perspective, the derivation of  Ku-band radar-only ice estimates
is not useful if coincident radiometer observations are available.

Shown in the bottom row of Figure \ref{f7} are the distributions of IWC gravity centers
estimated from lidar-only and radar-only observations as a function of their true values. Results are similar to those
obtained for IWP, in the sense that the radar-only retrieval distribution is bimodal and reliable only for ice clouds
with Ku-band radar observations above the detection threshold.
The lidar-only retrievals produce a much broader IWC gravity center distribution, with values that exhibit moderate 
correlation with the true IWC gravity centers.

\begin{figure}
    \centering
    \includegraphics[width=.481\linewidth]{Figs/fig07a.rev.png}
    \includegraphics[width=.481\linewidth]{Figs/fig07b.rev.png}
    \includegraphics[width=.481\linewidth]{Figs/fig07c.rev.png}
    \includegraphics[width=.481\linewidth]{Figs/fig07d.rev.png}
    \caption{Top Row: Density plots of IWP retrievals from lidar-only (left), and radar-only (right) observations as a function
    of true IWP. Bottom Row: Same as in the top row but for IWC gravity center.}\label{f7}
\end{figure}

\subsection{Synergistic retrievals}

@@

Shown in Figure \ref{f8} is the distribution of the synergistic IWP estimates as a function of their true
values.  As apparent in the figure, the synergistic IWP estimates are more accurate than the radiometer-only
estimates. At the same time, as apparent in Figure \ref{f9}, the retrieved conditional mean IWC for the 
18 classes described section 2a and shown in Figure \ref{f1} are in significantly better
agreement with the true IWC profiles than those derived from radiometer-only observations.  Moreover,
as seen in Figure \ref{f10} the synergistic IWC gravity center estimates are in much better agreement with 
the true IWC gravity center than those derived from single-instrument observations.
